---
title: "Credit Card Balance; Who is More in Debts"
author: "Nima Niarad"
date: "7/22/2021"
output:
  rmarkdown::github_document: default
  rmarkdowngithub_document: default
---

<style> body {text-align: justify} </style> <!-- Justify text. -->

## Part D - Conclusion

In this project, I have analyzed the credit card balance. 

I have shown which variables play a key role and have more impact on the balance to be included in the model. There are ten variables to be investigated the relationships between them and the main dependent variable, Balance. 

After plotting them to know what are the relationships, I decided to begin with Married, Education, Age, Income, Limit, and Student in multiple linear regression.

Gradually, with trying different kinds of models, I found out that Age, Married, and Education are not
statistically significant and should be removed from the model. 

There was a non-linearity between Limit and Balance, also Limit and Income were correlated. So, I tried some high order
equations with the intersection of Limit and Income. Because Limit and Income were connected and Limit
behave in a non-linear way with Balance, I also tried the intersection with high orders. 

The last model in Part B with minimum standard and residual error, and also R-squared close to one (it
interpret about the 96 percent of variability which was great!) is the best one.

However, just counting on R-squared is not a wise approach. That is why I investigate the models with
better techniques Part C. 

Three main tests were applied; the validation set approach. LOOCV, and K-fold cross-validation. 

Using the first one to prove that I was right about the best model. The second
and the third test are almost the same approach with K-fold is slightly better in some aspects. By using
the second and third methods, I figured it out if I go further in terms of high orders, the model will not be 
improved. It turned out the third degree is the best one. 


Now that I have selected the best model, it is time to interpret what happens between Balance and other variables.

```{r, warning=FALSE, results='hide'}
library(readr)
Credit <- read_csv("C:/Nima/Rstudio/Git/Credit Card Balance; Who is More in Debts/Credit-Card-Balance--Who-is-More-in-Debts-/Credit.csv")

```

```{r}
Model.Final = lm(Balance ~ Income + Limit + I((Income*Limit)^3)+ I(Limit^3)+ Student, data = Credit)
coef(Model.Final)
```



The Income coefficient telling me if an individual has one dollar more income, their balance will be
decreasing by 8 dollars. In other words, rich people are supposed to be less in debt to banks which are sounds
logical, but it seems it is not the whole story! When I look at the limit, understand that if somebody s
limit is one dollar higher, they have about 0.215 dollars more balance. The coefficient of the intersection
of Income and Limit and Limit with the power of three is small! I cannot expect a lot of influences from
them. On the other hand, students play a key role. If you are a student, you are four
and a half dollars more in debt in comparison to non-students. As a result, individuals who are both rich
and student can manage their balances better. However, the most reliable persons here are rich people who are
not students, they are less than the others in debt to the banks.
It would be suggested that banks give a high limit to rich people, but students are not reliable to give them
credit cards with high limits. I need more data regrading what percentage of people are both rich and
students. Even their universities are important, public or private or if students have a part-time
job are less in debt or the ones who have rich parents are more reliable!


